Bioinformatics analysis of whole-genome bisulfite-sequencing data

### 2014-12-05 Rmarkdown/wgbs_bioinformatics_analysis.Rmd
Added example of methtuple output

Most methylation callers, such as `Bismark` and `Bis-SNP`, perform methylation calling at single methylation loci, which I refer to as 1-tuples. The output file is a table, where each row records the co-ordinates of a cytosine and the number of methylated and unmethylated reads at that position. Table \ref{tab:1-tuples} is representative of the type of data returned by these programs. The file format is generally tab-delimited plain text, the Browser Extensible Data (BED) format or the Variant Call Format (VCF).

@@

\subsection{Methods}

@@

>>>>

Most methylation callers, such as `bismark_methylation_extractor` and `Bis-SNP`, perform methylation calling at single methylation loci, which I refer to as 1-tuples. The output file is a table, where each row records the co-ordinates of a cytosine and the number of methylated and unmethylated reads at that position. Table \ref{tab:1-tuples} is representative of the type of data returned by these programs. The file format is generally tab-delimited plain text, the Browser Extensible Data (BED) format or the Variant Call Format (VCF).

@@

\subsection{Methods}\label{sec:methtuple_methods}

@@

The output format of `methtuple` is tab-delimited plain text, optionally compressed with `gzip` or `bzip2`. An example of the output is shown below for 3-tuples:

```
chr     strand  pos1    pos2    pos3    MMM     MMU     MUM     MUU     UMM     UMU     UUM     UUU
chr1    +       469     471     484     0       0       4       1       1       0       0       0
chr1    +       471     484     489     1       0       0       0       2       2       1       0

```

__TODO: Show example of `methtuple` output__
